%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Backend Engineer} % Job title
{Boostsecurity.io (startup company)} % Organization
{Montreal, Canada} % Location
{Jan. 2023 - Oct. 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
	\item {Worked on backend software development and API-based data integration to provide early detection and remediation of security vulnerabilities along the customer's software lifecycle (application code, SCM setup, CI/CD, package dependencies, testing, deployment).}
	\item{Core skills: Scrum, Python, REST-API, GraphQL, Docker, Kafka, CI/CD, AWS, Microservices, SQL and Neo4J.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Software Developer} % Job title
{SERPRO} % Organization
{Salvador, Brazil} % Location
{Mar. 2014 - Jan. 2023} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
	\item{Implemented a data pipeline (mixed cloud and on-premise), to automate legal document ingestion, processing, and classification.}
	\item{Reduced by 30\% the cycle time of an important pipeline (40GB+ per cycle) that prepares and distributes legal processes for judgment in several units of Brazil’s Federal Revenue Service.}
	\item{Worked on backend software development projects for the Brazilian Federal Government to provide full-text query services for legal documents (1Mi+ documents indexed).}
	\item{Developed a text classifier for legal documents based on NLP techniques.}
	\item{Core skills: Scrum, Python, REST-API, Airflow, MongoDB, Docker, CI/CD, AWS, NumPy, Pandas, NLP, Apache Lucene, Java.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Data Engineer} % Job title
{INDRA} % Organization
{Salvador, Brazil} % Location
{Jul. 2012 - Mar. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
	\item{Provided support to a 10TB 24/7 database infrastructure, running massive OLTP and large OLAP systems.}
	\item{Successfully designed and implemented a complex data warehouse infrastructure to provide analytical information over a 5Bi+ rows database related to income tax information.}
	\item{Core skills: Scrum, MS SQL Server 2005, Transact-SQL, Data Warehousing, ETL, SQL Server Integration Services (SSIS).}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Backend Engineer} % Job title
{F4IT (startup company)} % Organization
{Salvador, Brazil \& Zurich, Switzerland} % Location
{Apr. 2011 - Jul. 2012} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
	\item{Maintened and optimized database routines of QuartalCommission (from Switzerland), an investment fund management system for commission calculation and payment. Used by HSBC, CITIBANK, ABN, and UBS banks.}
	\item{Core skills: Scrum, Oracle PL/SQL}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Business Intelligence Team Leader} % Job title
{RMS Software} % Organization
{Salvador, Brazil} % Location
{Feb. 2010 - Abr. 2011} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
	\item{Responsible for the Business Intelligence module of RMS (a retail ERP software) for 80+ customers in Brazil and Europe.}
	\item{Core skills: Data Modeling, Data Warehousing, ETL, Oracle PL/SQL, Microstrategy.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{ETL Developer} % Job title
{CPM Braxis} % Organization
{Salvador, Brazil} % Location
{Dec. 2003 - Feb. 2010} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{Offshore development and maintenance of an ETL system.} 
\item{ETL architecture definition to support massive financial report generation.} 
\item{Data warehouse dimensional modeling adopting a ROLAP approach.}
\item{Team integration, including members from Canada, the USA, and Netherlands.}
\item{Core skills: Data Modeling, Data Warehousing, ETL, Oracle PL/SQL, Oracle Data Integrator (ODI).}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Database Administrator} % Job title
{Unitech} % Organization
{Salvador, Brazil} % Location
{Dec. 1998 - Dec. 2003} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
	\item{Database cluster installation and maintenance.}
	\item{Data replication for 36 remote sites.} 
	\item{Database migration planning and execution.}
	\item{Best practices definition for Transact-SQL programming.}
	\item{Transact-SQL programming.}
	\item{Data warehouse dimensional modeling.}
	\item{Core skills: Microsoft Cluster Service (MSCS), MS SQL Server 2000, Data Replication.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}